---
title: "droughtmonitor: access data from U.S. Drought Monitor"

output:
  github_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
library(knitr)
library(dplyr)
library(devtools)
load_all()
```


[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#WIP)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#experimental)


## Introduction
`droughtmonitor` allows users to access [U.S. Drought Monitor's](https://droughtmonitor.unl.edu/) publicly available data. The package provides a set of functions to easily navigate through and obtain drought related data provided by the organization. 


## Examples

### Example: Return comprehensive statistics for Sacramento County, CA 
The following code returns comprehensive statistics by week from January 1st, 2020 to December 31st, 2020. Comprehensive statistics include ...
```{r}
data <- monitor_drought(aoi = "06067",
                        var = "cs",
                        start_date = "1/1/2020",
                        end_date = "12/31/2020")
data

# The following are ways to obtain the same data 
data <- monitor_drought(aoi = "6067", # robust to omitting the leading 0
                        var = "cs",
                        start_date = "1/1/2020",
                        end_date = "12/31/2020")

# specifying the year argument is an easier way to get data for an entire year
data <- monitor_drought(aoi = "6067",
                        var = "cs",
                        year = 2020) 

# note that map releases do not always correspond to the first and last days
# of the year, meaning the returned data may be slightly outside the 
# specified year(s). For example, in this case the minimum map dates is 
# December 31st  of the previous year. 
summary(data$MapDate)


# The year argument can also be specified as a range for multiple years of data
data <- monitor_drought(aoi = "06067",
                        var = "cs",
                        year = 2020:2021) 


```

### Example: 



